---
title: plotit!
date: ""
output: github_document
---
<style> body {text-align: justify} </style>

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)


```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, eval = FALSE, comment = "#>")
```


[plotit](https://bautheac.github.io/plotit/) belongs to the [finRes](https://bautheac.github.io/finRes/) suite where it provides visualization solutions for packages including, at the time of writing, [pullit](https://bautheac.github.io/pullit/) and [factorem](https://bautheac.github.io/factorem/). Install the development version from github with `devtools::install_github("bautheac/plotit")`. 


## pullit
plotit provides plot methods for a number of pullit objects including, at the time of writing, futures term structure (\linkS4class{FuturesTS}) and fund market (\linkS4class{FundMarket}) objects.

### Futures term structure
Plot a futures series term structure dynamics with:
```{r `plot fund term structure`}
library(plotit); library(pullit); library(lubridate)

end <- Sys.Date(); start <- end - years(2L)
tickers <- c("C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
             "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", 
             "KCA Comdty", "KWA Comdty", "LBA Comdty", "LCA Comdty", 
             "LHA Comdty", "NGA Comdty", "O A Comdty", "PAA Comdty", 
              "S A Comdty", "SIA Comdty", "W A Comdty", "XBA Comdty")

futures_TS <- pull_futures_market(source = "Bloomberg", type = "term structure", active_contract_tickers = tickers, 
                                  start, end, TS_positions = 1L:5L, roll_type = "A", roll_days = 0L, 
                                  roll_months = 0L, roll_adjustment = "N", verbose = FALSE)

plot(object = futures_TS, ticker = "C A Comdty")
```

### Fund market
Plot historical fund performance with:
```{r `plot fund performance`}
tickers <- c("SPY US Equity", "GLD US Equity", "EEM US Equity")

fund_market <- pull_fund_market(source = "Bloomberg", fund_tickers, start, end, verbose = FALSE)

plot(object = fund_market, ticker = "GLD US Equity")
```


## factorem

### Performance overview
```{r `plot factor performance`}
ranking_period = 1L

factor <- OI_nearby_factor(data = futures_TS, ranking_period = ranking_period)

plot(factor, type = "performance")
```

### Positions overview
```{r `plot factor positions`}
plot(factor, type = "positions")
```
