---
title: plotit!
date: ""
output: github_document
---
<style> body {text-align: justify} </style>

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)


```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, eval = FALSE, comment = "#>", message = FALSE, warning = FALSE)
path <- here::here("development", "storethat.sqlite")
```


[plotit](https://bautheac.github.io/plotit/) belongs to the [finRes](https://bautheac.github.io/finRes/) suite where it provides visualization solutions for packages including, at the time of writing, [pullit](https://bautheac.github.io/pullit/) and [factorem](https://bautheac.github.io/factorem/).  
Install the development version from github with `devtools::install_github("bautheac/plotit")`. 


## pullit
[plotit](https://bautheac.github.io/plotit/) provides plot methods for a number of [pullit](https://bautheac.github.io/pullit/) objects including, at the time of writing, futures term structure (FuturesTS) and fund market (FundMarket) objects.

### Futures term structure
Plot a futures series term structure dynamics with:
```{r `plot futures term structure`}
library(plotit); library(pullit); library(factorem); library(lubridate)

start <- "2016-01-01"; end <- "2017-12-31"
ticker <- "C A Comdty"

data <- pull_futures_market(
  source = "storethat", type = "term structure", active_contract_tickers = ticker,
  start, end, TS_positions = 1L:5L, roll_type = "A", roll_days = 0L,
  roll_months = 0L, roll_adjustment = "N", verbose = FALSE, file = path
  )

plot(object = data, ticker = ticker)
```

### Fund market
Plot historical fund performance with:
```{r `plot fund performance`}
ticker <- "SPY US Equity"

data <- pull_fund_market(
  source = "storethat", ticker, start, end, verbose = FALSE, file = path
  )

plot(object = data, ticker = ticker)
```


## factorem
Similarly [plotit](https://bautheac.github.io/plotit/) provides plot methods for [factorem](https://bautheac.github.io/factorem/) factor objects (AssetPricingFactor).

### Performance overview
Plot historical factor performance with:
```{r `plot factor performance`}
tickers <- c(
  "LZB US Equity", "SGA US Equity", "AGCO US Equity", "CLR US Equity",
  "GHC US Equity", "MAN US Equity", "SITE US Equity", "AJRD US Equity",
  "COMM US Equity", "GME US Equity", "MEI US Equity", "SMP US Equity"
  )

data <- pull_equity_market(
  source = "storethat", tickers = tickers, start = start, end = end, 
  verbose = F, file = path
  )

ranking_period <- 1L

factor <- factorem(
  name = "momentum", data = pullit::get_data(data),
  sort_levels = FALSE, weighted = FALSE, ranking_period = ranking_period
  )

plot(factor, type = "performance")
```

### Positions overview
Plot factor positions statistics with:
```{r `plot factor positions`}
plot(factor, type = "positions")
```
